% !TEX root = ./discussion-example.tex
% !TEX program = latexmk
\makeatletter
\def\input@path{{./}{../}{../../}{../../../}{../../../../}}
\makeatother
% Example discussion capture demonstrating the intake macros.
\def\MathNotesDocTitle{Discussion Notes Example}
\def\MathNotesDocAuthor{MATH 2243}
\def\MathNotesDocDate{2025-10-21}
% Uncomment to mirror section titles in the header:
% \def\MathNotesDocHeader{\MakeUppercase{\leftmark}}
\input{tex/system/document-notes.tex}

\newdiscussion{<pack here>}{<sheet or topic>}{<YYYY-MM-DD>}
\DiscussionSection[sec:discussion-warmup]{Warm-up Drill}
\DiscussionPoint{Capture the raw bullet points from the session.}
\DiscussionPoint[Tag]{Use the optional label to add a cue such as Warm-up/Action.}
\DiscussionSection[sec:discussion-main]{Main Worksheet}
\DiscussionPoint{Call back to earlier sections with \cref{sec:discussion-warmup} to keep continuity.}
\DiscussionPoint[Check]{Note any grading or rubric cues.}
\closenotes

\begin{DiscussionDefinition}[Optional subtitle]\label{disc:def:intake}
Use this grayscale box for quick definitions or terminology that surfaced during
the discussion.
\end{DiscussionDefinition}

\begin{DiscussionTheorem}[Optional subtitle]\label{disc:thm:intake}
Drop rules-of-thumb or impromptu proofs here.
\end{DiscussionTheorem}

\begin{DiscussionExample}[Optional subtitle]\label{disc:ex:intake}
Keep scratch calculations or sketches near the discussion log.
\end{DiscussionExample}

\textit{Tip:} Add labels (\InlineCode{\label\{...\}}) inside any block to make
cross-referencing easy, e.g., \cref{disc:def:intake}.

\newdiscprob{W7}{Q3}[GBW warm-up]
Estimate the settling time for a 1\% error band when the amplifier from \cref{fig:notes-main-plot}
drives a unit-step input. Reference \cref{def:notes-gain-bandwidth} for terminology.
\begin{solution}
Approximate the closed-loop response with the dominant pole from \cref{thm:notes-single-pole} and apply
the standard $4/\zeta\omega_n$ heuristic. Compare the estimate with the measured values in the lecture log.
\end{solution}
\end{discproblem}

\MathNotesDocumentEnd
